---
title: "NUM~CAT anova"
author: "Dr K"
date: "fall 2020"
output:
  html_document:
    df_print: paged
---

```{r include=FALSE,echo=FALSE}
require(knitr)
require(tidyverse)
require(tigerstats)

```

```{r initial-setup, eval=T, echo=FALSE, include=FALSE}
#install.packages('reticulate')
reticulate::virtualenv_create('testEnv')
reticulate::use_virtualenv('testEnv')
reticulate::virtualenv_install('testEnv', packages = 'numpy')
reticulate::virtualenv_install('testEnv', packages = 'plotnine')
reticulate::virtualenv_install('testEnv', packages = 'pandas')
reticulate::virtualenv_install('testEnv', packages = 'scipy')
reticulate::virtualenv_install('testEnv', packages = 'pingouin')

```

## Setup Block
```{r setup, include=TRUE}
knitr::opts_chunk$set(echo = TRUE)
library(reticulate)
reticulate::use_virtualenv('testEnv')
```


```{python}
import pandas as pd
GSS = pd.read_csv('GSScsv.csv')
type(GSS)
GSS.columns
```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->

The data is in the file GSScsv.csv and came from the 2018 General Social Survey.  The question to answer is to resolve this hypothesis.  
$H_0$ There is no difference between the average score on the WORDSUM test and level of schooling DEGREE  
$H_a$ There is a significant difference in average score on the WORDSUM test between at least two levels of DEGREE  

# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->

# Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{python}
from plotnine import * 
#GSS.boxplot(column='WORDSUM',by= 'DEGREE')
#plt.show()
ggplot(GSS) + aes(x='DEGREE', y = 'WORDSUM')+geom_boxplot() + theme(
    #panel_background=element_rect(fill=gray, alpha=.2),
    #dpi=120,
    figure_size=(8, 8), # inches
    aspect_ratio=1/3    # height:width
)

```

### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{python}
GSS.groupby("DEGREE")['WORDSUM'].describe().reset_index()	
```

## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->


```{python}
import pingouin as pg
import pandas as pd
import numpy as np


#perform Welch's ANOVA
pg.welch_anova(dv='WORDSUM', between='DEGREE', data=GSS)

```


```{python}
pg.pairwise_tukey(dv='WORDSUM', between='DEGREE', data=GSS)
```


# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->
